### 2025-06-12 basic-statistics.qmd
20250612 - coefficient of determination

where $y$ is the [outcome variable](#sec-correlationalStudy), $y_i$ is the observed value of the [outcome variable](#sec-correlationalStudy) for the $i$th observation, $\hat{y}_i$ is the model predicted value for the $i$th observation, $\bar{y}$ is the mean of the observed values of the [outcome variable](#sec-correlationalStudy).
The total sum of squares is an index of the total variation in the [outcome variable](#sec-correlationalStudy).

>>>>

where $y$ is the [outcome variable](#sec-correlationalStudy), $y_i$ is the observed value of the [outcome variable](#sec-correlationalStudy) for the $i$th observation, $\hat{y}_i$ is the model predicted value for the $i$th observation, and $\bar{y}$ is the mean of the observed values of the [outcome variable](#sec-correlationalStudy).
The total sum of squares is an index of the total variation in the [outcome variable](#sec-correlationalStudy).

The coefficient of determination typically ranges from 0 to 1, but it can be negative.
A negative coefficient of determination indicates that the predicted values are less accurate than using the mean of the actual values as the predicted values (i.e., predicting the mean of the observed values for every case).
